Read the data. Pay attention that data has NA values. It's better to convert target variable to factor.
```{r}
data <- read.csv("donner_party.csv")
# delete data that have NA values
data <- na.omit(data)
# convert target variable (Survived) to factor
data$Survived<-as.factor(data$Survived)
head(data)
```

For prediction we will use only variables `Sex` and `Age`. 

For predicting binary outcome we will use **Generalized Linear Model** (`method = "glm"`) and **caret package**. 

```{r}
# code for regression
library("caret")
# train model using Generalized Linear Model
model <- train(Survived ~ Sex + Age, method="glm", data=data)
prediction <-predict(model, data)
```

What is your in-sample accuracy? Build a confusion matrix

```{r}
# code for confusion matrix
confusionMatrix(prediction, data$Survived)
```

Use a cross-validation with `method = "repeatedcv"`, `number = 5`, `repeats = 10`. Does cross-validation improve the accuracy?

```{r}
# code for cross-validation
# train new model using cross-validation
model2 <- train(Survived ~ Sex + Age, method="glm", data=data, trControl=trainControl(method="repeatedcv", number=5, repeats=10))
prediction2 <- predict(model2, data)
confusionMatrix(prediction2, data$Survived)
```
**Unfortunately, cross-vallidation didn't improve the accuracy**